### 2021-11-23 draft.tex
Deploying to gh-pages from @ gottacatchenall/thesis_proposal@136bef76216683e27eb23d74f75d01a00a22fcea 🚀

\begin{figure}
\hypertarget{fig:thesis}{%
\centering
\includegraphics{./figures/thesisconcept.png}
\caption{thesis concept}\label{fig:thesis}
}
\end{figure}

@@

>>>>

\begin{figure}
\hypertarget{fig:thesis}{%
\centering
\includegraphics{./figures/thesisconcept.png}
\caption{Left: a framework for ecosystem monitoring, forecasting, and
mitigation. From the top, a set of biodiversity observatories which form
a monitoring network. Each collect various biodiversity data products.
From this raw data, we derive essential biodiversity variables (EBVs),
and forecast how they change over time. Based on this forecast, we wish
to choose the best possible mitigation strategy to maximize the chance
the realized future outcomes of the EBV approaches the target state.
Right: Each panel represents a chapter of the thesis, which follows the
flow of the framework on the left.}\label{fig:thesis}
}
\end{figure}

@@

By using the success of numerical-weather prediction and the Earth
monitoring system that supports it as a model,
